Manuscript

### 2022-02-03 analysis/manuscript.Rmd
wflow_publish("analysis/manuscript.Rmd")

# Heterogeneity stats

@@

>>>>

# Heterogeneity stats.

@@

## Paths summary.

A summary of the $\omega$, $\rho$, $\gamma$ and $\rho_{resid} + \gamma$ estimates are summarized in the table below. Those with BF-significant differences between the estimates (according to a Z-test, p < 0.05/`r dim(data)[1]`) are given as T/F in the last three columns.

```{r paths_summary, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE), echo = FALSE}

paths_summary <- data %>% dplyr::select(exposure_description, outcome_description, gam_beta, rho_beta, omega_beta, gam_rho_resid, gam_vs_rho_BF_sig, omega_vs_rho_BF_sig, omega_vs_gam_BF_sig)

format_round_cols <- colnames(dplyr::select_if(paths_summary, is.numeric))

DT::datatable(paths_summary, width = "100%") %>% formatRound(columns=format_round_cols, digits = 3)
